\problemname{Limbo}

\noindent Dominick Cobb and Arthur are "extractors", who perform corporate espionage using an experimental military technology to infiltrate the subconscious of their targets and extract valuable information through a shared dream world. Cobb and his entourage are contacted by a mysterious Japanese syndicate and given a seemingly impossible task: instead of extracting information, do the opposite - plant an idea in someone's mind. Cobb notes that when using dream-sharing technology, time slows by different factors down depending on whose dream they enter. Their target is to convince Cepshun, the heir of an energy conglomerate, to dissolve his father's company. Before Cobb starts, he notes that it would be important to figure out the passage of time to allocate adequate for the operation to be completed.\\

\noindent In Cepshun's dreams, there are multiple different layers of consciousness, each of which controls a different area of Cepshun's dreams and memories. Cobb needs to move between several dreams to reach his destination dream - some of them belonging to Cepshun, and some of them belonging to his entourage. He notes that entering the dream of the host allows Cobb's gang to move downwards a level, while entering a dream that isn't Cepshun's allows them to move rightwards - forming a rather unusual triangle. \\

\noindent 1 3 6 10\\
 2 5 9\\
 4 8\\
 7\\

\noindent Cobb wants to know how much time slows down by inside his target dream, given how far they need to travel rightwards, $R$, and downwards, $D$. \\

\section*{Input}
The input will be a single line consisting of 2 numbers; $R$ and $D$ where $1 \leq R, D \leq 2^{31} - 1$ specifying how far right and down the target dream is.

\section*{Output}
Output the factor at which time slows down by in the target dream.