\problemname{Thanos}

\noindent Dr. Thanos, a data scientist and nihilist, recently published a paper titled "The Snapping Point of the Universe: Why Population Growth Points to Imminent Destruction", where he outlines his theories on the effect of overpopulation on various star systems and their adverse effects on living conditions and the overall happiness of the population. He is convinced that these new findings can lead to sweeping reforms in intergalactic law, and lead to a better quality of life for all lifeforms.\\

\noindent Thanos turns to you, his confidant, and asks that you do some investigation for him so that he has some examples to point to when he presents his findings to the Association of VENGE's Research Society. The society, one of the galatic leaders in egalitarianism and social justice, is usually steadfast and hesitant for change, so Thanos is convinced that they are going to be a tough crowd. He asks you to investigate several datasets and see if they could be potentially helpful in supporting his argument.\\

\noindent Thanos' research assistant hands you information regarding several planets. On each file, you see the current population, population growth rate, resources available to the population, and population resource consumption. Given this information, your job is to find out the number of years the planet has left before the population is no longer sustainable.\\

\noindent You are given n, the number of planets to analyze. The following four numbers, w, x, y, z, represent:\\
w - the current population\\
x - the population growth rate\\
y - the yearly production of resources\\
z - the amount of required per citizen, per year\\

\noindent For each planetary study, Thanos desires to know the number of years it will take before the planet is no longer sustainable for its population.\\

\section*{Input}
The input will be $n$+1 lines, the first line, $n$, describes the number of planets to analyze.
The remaining $n$ lines each have single line consisting of 4 numbers; $w$, $x$, $y$, and $z$ where $1 \leq w, x, y, z \leq 2^{31} - 1$ where each is a metric of planetary study as described above.

\section*{Output}
Output the number of years the planet has before it is no longer sustainable for its population.